### 2014-05-21 Paper1/paper1.tex
Mild update

% Please keep the abstract between 250 and 300 words
\section*{Abstract}
We derive a novel modeling approach for determining movement intent from a force-disturbed planar arm trajectory, examine its parameter sensitivity, and test it on human reaching data. While we demonstrate that popular modeling approaches can be algebraically inverted to yield the same result, this more general approach reveals strengths, limitations, and underlying assumptions. After populating our model with measured lengths and masses as well as impedance values from the literature, we perform sensitivity analysis to determine the accuracy of the model relative to the uncertainty naturally inherent in point-to-point reaching. We find that sensitivity to parameter inaccuracy is on the order of microns and lower than the inaccuracy of human reaching. Further, most of the sensitivity results from uncertainty with regard to the stiffness of the joints. The robustness of this approach indicated that it was suitable for determining reaching intent from human point-to-point reaching movements disturbed by large force pulses. Intended trajectory showed no change from undisturbed reaching for 150 ms after the onset of disturbance. Beyond this point, stiffening of the arm, change in intent, or both usually lead to deviation from undisturbed reaching. Not all disturbed reaches showed evidence of change in intent. Unlike $\lambda$ models, the reaching intent determined by our model is physiologically plausible. This success allows real-time determination of error that can free learning enhancement and treatment methods like error augmentation and challenge point from needing to prescribe explicit task goals. In addition, extraction from recorded human motion enables direct inspection of and hypothesis testing on the contents of human motor intent. While not explicitly examined, this approach is also valid for determination intent is more complex situations like team sports and national security.

>>>>

% Please keep the abstract between 250 and 300 words
\section*{Abstract}
We derive a novel modeling approach for determining movement intent from force-disturbed arm movement, examine its parameter sensitivity, and validate it on human reaching data. We demonstrate that inverting popular arm modeling approaches algebraically allows determination of movement intent from recordings of force disturbances and arm movement. We then extend this to a more general approach reveals strengths, limitations, and underlying assumptions. After populating our model with measured lengths and masses as well as impedance values from the literature, we perform sensitivity analysis to determine the accuracy of the model relative to the uncertainty naturally inherent in point-to-point reaching. We find that sensitivity to parameter inaccuracy is on the order of microns and lower than the inaccuracy of human reaching. Further, most of the sensitivity results from uncertainty with regard to the stiffness of the joints. The robustness of this approach indicated that it was suitable for determining reaching intent from human point-to-point reaching movements disturbed by large force pulses. Intended trajectory showed no change from undisturbed reaching for 150 ms after the onset of disturbance. Beyond this point, stiffening of the arm, change in intent, or both usually lead to deviation from undisturbed reaching. Not all disturbed reaches showed evidence of change in intent. Unlike $\lambda$ models, the reaching intent determined by our model is physiologically plausible. This success allows real-time determination of error that can free learning enhancement and treatment methods like error augmentation and challenge point from needing to prescribe explicit task goals. In addition, extraction from recorded human motion enables direct inspection of and hypothesis testing on the contents of human motor intent. While not explicitly examined, this approach is also valid for determination intent is more complex situations like team sports and national security.
